\thetitle\\ \vspace{0.2em} \LARGE{On The Inadequacy of Uniform Modeling for WLAN Workloads}

### 2008-01-20 models.tex
Minor tweaks.

\multicolumn{1}{c}{\textbf{Description}} \\[2pt]

@@

\raisebox{1.5pt}{$\centerdot$} session start time randomly chosen from viable range

@@

\raisebox{1.5pt}{$\centerdot$} packet sizes and intervals are drawn from inherited parametric distributions

>>>>

\multicolumn{1}{c}{\textbf{Overridden and inherited properties}} \\[2pt]

@@

\raisebox{1.5pt}{$\centerdot$} session start time assigned according to Poisson arrival model

@@

\raisebox{1.5pt}{$\centerdot$} packet sizes and intervals are drawn from fitted Exponential distributions
